Hidden Talents Multiverse Analysis

### 2021-06-28 README.Rmd
another attempt to fix tables for OSF

---
title: "Hidden Talents Multiverse Analysis"
output: github_document
---

@@

library(tidyverse)
library(gt)
```

@@

    tibble(
      dir       = x %>% str_remove_all("scripts/") %>% str_remove_all("/.*") %>% str_remove("^\\d-"),
      script    = x %>% str_remove_all(".*/"),
      raw       = script_text %>% str_squish() %>% str_c(collapse = ", "),
      n_input   = str_count(script_text[1], "input"),
      input1    = script_text[1],
      input2    = input1 %>% str_remove_all("input: ") %>% str_trim(),
      input     = input2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = ", ") %>% ifelse(. == ", ","",.),
      n_output  = str_count(script_text[2], "output") %>% ifelse(is.na(.), 0, .),
      output1   = script_text[2],
      output2   = output1 %>% str_remove_all("output: ") %>% str_trim(),
      output    = output2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = ", ") %>%  ifelse(. == ", NA","",.)
    )
  }) 
```

@@

cat(
  "|script|input|output|",
  "|------|-----|------|",
  glue::glue_data(
    data_prep,
    "|{script}|{input}|{output}|"
  ),
  sep = "\n"
)
```

>>>>

---
title: "Hidden Talents Multiverse Analysis"
output: md_document
---

@@

library(tidyverse)
library(gt)
library(glue)
library(htmltools)
```

@@

    tibble(
      dir       = x %>% str_remove_all("scripts/") %>% str_remove_all("/.*") %>% str_remove("^\\d-"),
      script    = x %>% str_remove_all(".*/"),
      raw       = script_text %>% str_squish() %>% str_c(collapse = ", "),
      n_input   = str_count(script_text[1], "input"),
      input1    = script_text[1],
      input2    = input1 %>% str_remove_all("input: ") %>% str_trim(),
      input     = input2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = "<br> ") %>% ifelse(. == "<br> ","",.),
      n_output  = str_count(script_text[2], "output") %>% ifelse(is.na(.), 0, .),
      output1   = script_text[2],
      output2   = output1 %>% str_remove_all("output: ") %>% str_trim(),
      output    = output2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = "<br> ") %>%  ifelse(. == "<br> NA","",.)
    )
  }) 
```

@@

cat(
  "|script|input|output|",
  "|------|-----|------|",
  glue::glue_data(
    data_prep,
    "|{script}|{input}|{output}|"
  ),
  sep = "\n "
)
```
